Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-12 paper.tex
Final changes for now

We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{\rm ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K. A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40. A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260. Outside of these mass ranges, the Pop III star dies as a black hole. In this simulation, no black hole physics are implemented, so the Pop III star simply turns into an inert collisionless particle. When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg. From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40, the star dies as a hypernova with energies taken from \citet{Nomoto06}. The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12.

@@

%====================================================================
\subsection{Variations in the halo masses at collapse}
\label{sec:variations}
%====================================================================
Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity. However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the mininum. We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation. There are three main causes of this significant variation in mass. First, a fraction of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.  Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs. Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.  Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}. This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}. Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small effect in some halos where the local LW radiation flucutations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.  In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.  The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.

>>>>

We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{\rm ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K. A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40. A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260. Outside of these mass ranges, the Pop III star dies as a black hole. In this simulation, no black hole physics are implemented, so the Pop III star simply turns into an inert collisionless particle. When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg. From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40, the star dies as a hypernova with energies taken from \citet{Nomoto06}. The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12. \textbf{With our chosen IMF (Eq. \ref{IMF}), XX, XX, and XX per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.} \jhw{Fill in percentages}

@@

%====================================================================
\subsection{Variations in the halo masses at collapse}
\label{sec:variations}
%====================================================================
Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity. However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the mininum. We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation. There are three main causes of this significant variation in mass. First, a fraction \jhw{Give number} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.  Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs. Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.  Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}. This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}. Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small effect in some halos where the local LW radiation flucutations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.  In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.  The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.

### 2019-08-12 referee.tex
Final changes for now

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage{mdframed}

@@

In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.  The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).  In future studies, we will start at earlier times when the evolution is solidly in the linear regime.  We thank the referee for pointing this out.
q
\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

@@

The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}
-It's not immediately obvious to me how we would be able to estimate this. I would have to look at these processes in more detail to see if there are some mass ranges correlated with them. Any insight from John?

>>>>

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage{mdframed}
\parskip=10pt

@@

In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.  The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).  In future studies, we will start at earlier times when the evolution is solidly in the linear regime.  We thank the referee for pointing this out.

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

@@

The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}

This is an interesting question, but it is outside the scope of this paper.  It most likely depends on the large-scale environment, halo mass accretion history, and halo star formation history, but how these factors affect each other is unclear.  In practice, it would be difficult to determine the relative importance of dynamical heating and temporal LWBG fluctuations because of the time variations in the heating rate and suppression of H$_2$ cooling.  Because of these reasons, we do not give any estimates in the discussion.

The occurrence of BH formation and no metal enrichment depends on the chosen Pop III IMF, and we have addressed in an earlier answer and made a note in Section 2.2.1.
